---
title: "Regression Models Project"
author: "RH"
date: "December 7, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load the data and necessay package
```{r}
library(datasets)
library(ggplot2)
data("mtcars")
str(mtcars)
```

Convert variables of cyl, vs, am, gear and carb to factor variable to following analysis.
```{r}
mtcars$am   <- factor(mtcars$am,labels=c("Automatic","Manual"))
mtcars$cyl  <- factor(mtcars$cyl)
mtcars$vs   <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

#Simple linear regression model to exmaine mpg
```{r}
fit1 <- lm(mpg ~ am, mtcars)
summary(fit1)$coef
```
As is stated that the P-value of amManual variable is `r summary(fit1)$coef[2,4]`. This indicated that the difference between automatic and manual transmissions is significant.

We could also validate the result using t-test.
```{r}
mtcars_auto <- mtcars[mtcars$am=="Automatic", ]
mtcars_manual <- mtcars[mtcars$am=="Manual", ]
t.test(mtcars_auto$mpg, mtcars_manual$mpg)
```

#Multivariable regression model
First we include all the variables in the data set to examine the relationship between mpg and other variables to select proper variables to build the model.
```{r}
fit2 <- lm(mpg ~ ., mtcars)
summary(fit2)
```